Appendix

### 2024-08-30 manuscript/manuscript_appendix.Rmd
Further changes to the appendix.

```{r shifted-distributions-appendix, warning=FALSE, message=FALSE, fig.cap=cap}
cap <- paste0(
  "Invariant power transformation produces transformation parameters that are invariant to location and shape. ",
  "Samples were drawn from normal, right-skewed and left-skewed distributions, respectively, which then underwent a shift $d_{\\text{shift}}$ or multiplication by $d_{\\text{scale}}$. ",
  "Estimates of transformation parameter $\\lambda$ with the conventional power transformations (circle) show strong dependency on the overall location and scale of the distribution, ",
  "whereas estimates with the invariant power transformations (triangle) are constant."
)

>>>>

```{r shifted-distributions-appendix, warning=FALSE, message=FALSE, fig.cap=cap}
cap <- paste0(
  "Invariant power transformation produces transformation parameters that are invariant to location and scale. ",
  "Samples were drawn from normal, right-skewed and left-skewed distributions, respectively, which then underwent a shift $d_{\\text{shift}}$ or multiplication by $d_{\\text{scale}}$. ",
  "Estimates of the transformation parameter $\\lambda$ for the conventional power transformations show strong dependency on the overall location and scale of the distribution and the optimisation criterion, ",
  "whereas estimates obtained for the location- and scale-invariant power transformations are constant."
)
